Bird beak's elaboration and innovation

### 2023-05-11 Analysis/06-Figure_with_correlations.Rmd
Update 06-Figure_with_correlations.Rmd

y axis = levels
column 1 = correlation of e/i projected on the mega level
column 2 = correlation of e/i projected on the macro level
stars for significant correlation between means.

@@

## Plot the correlations
pdf("../Manuscript/Figures/correlations_fable.pdf")
par(mfrow = c(1,2))
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_mega_level, col = super_orders_col,
                y.axis = TRUE, plot.phylo = TRUE,
                main = "Elaboration and innovation\nat the mega level") 
par(mar = c(5, 2, 4, 6) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_level, col = super_orders_col,
                y.axis = FALSE, plot.phylo = FALSE,
                main = "Elaboration and innovation\nat the macro level")
dev.off()
```

>>>>

@@

## Plot the correlations
pdf("../Manuscript/Figures/correlations_fable.pdf")
par(mfrow = c(1,2))
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_mega_level, col = super_orders_col,
                y.axis = TRUE, plot.phylo = TRUE,
                main = "Species projected onto\nthe whole phylogeny VCV") 
par(mar = c(5, 2, 4, 6) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_level, col = super_orders_col,
                y.axis = FALSE, plot.phylo = FALSE,
                main = "Species projected onto\ntheir superorders' VCV")
dev.off()
```
